### 2022-07-26 src/text/2-package-subsections/maps.tex
Add some more detail to maps section

The geometry object defines the pixelization scheme and map boundaries. It also
provides methods to transform between sky and pixel coordinates. Maps consist
of a geometry instance together with a Numpy data array containing the corresponding
map values. Map axes contain a sequence of ordered values which define bins on
a given dimension, spatial or not. Map axes can have physical units attached to
them, as well as define non-linear spaced bins.

The sub-package provides a uniform API for the FITS World Coordinate System
(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).

@@

% itemize because it helps me write, could also just be paragraphs...
\paragraph{WCS:}
The FITS WCS pixelization supports a different
number of projections to represent celestial spherical coordinates in a regular
rectangular grid. Gammapy provides full support to data structures using this
pixelization scheme.

\paragraph{HEALPix:}
This pixelization provides a
subdivision of a sphere in which each pixel covers the same surface area as
every other pixel. As a consequence, however, pixel shapes are no longer
rectangular, or regular. \gammapy provides limited support to HEALPix-based
maps, relying in some cases on projections to a local WCS grid.

\paragraph{Region:} In this case, instead of a fine spatial grid
dividing a rectangular sky region, the spatial dimension is reduced to a single
bin with an arbitrary shape, describing a region in the sky with that same
shape. Typically they are is used together with a non-spatial dimension, for
example an energy axis, to represent how a quantity varies in that dimension
inside the corresponding region.

>>>>

The geometry object defines the pixelization scheme and map boundaries. It also
provides methods to transform between sky and pixel coordinates. Maps consist
of a geometry instance together with a Numpy data array containing the corresponding
map values. Map axes contain a sequence of ordered values which define bins on
a given dimension, spatial or not. Map axes can have physical units attached to
them, as well as define non-linear spaced bins. All map classes support operations such
as arithmetic operations with unit support, up- and downsampling along
extra axes, interpolation, resampling of extra axes, interactive visualisation
in notebooks and interpolation onto different geometries.

The sub-package provides a uniform API for the FITS World Coordinate System
(WCS), the HEALPix pixelization and region-based data structure
(see Figure~\ref{ig*:minted:gp_maps}).

@@

% itemize because it helps me write, could also just be paragraphs...
\subsubsection{WCS Maps}
The FITS WCS pixelization supports a different number of projections to
represent celestial spherical coordinates in a regular rectangular grid.
Gammapy provides full support to data structures using this pixelization
scheme. For details see ~\cite{Calabretta2002}. This pixelisation
is typically used for smaller regions of interests, such as pointed
observations.

\subsubsection{HEALPix Maps}
This pixelization scheme ~\citep{Calabretta2002} provides a
subdivision of a sphere in which each pixel covers the same surface area as
every other pixel. As a consequence, however, pixel shapes are no longer
rectangular, or regular.
This pixelisation is typically used for all-sky data, such as data
from the \hawc or \fermi observatory. \gammapy natively supports
the multiscale definiton of the HEALPix pixelisation and thus
allows for easy up and downsampling of the data. In addition to
the all-sky map, \gammapy also supports a local HEALPix
pixelisation where the size of the map is constrained to a given
radius.
For local nighbourhood operations, such as convolution \gammapy relies
on projecting the HEALPix data to a local tangential WCS grid.

\subsubsection{Region Maps}
In this case, instead of a fine spatial grid
dividing a rectangular sky region, the spatial dimension is reduced to a single
bin with an arbitrary shape, describing a region in the sky with that same
shape. Typically they are is used together with a non-spatial dimension, for
example an energy axis, to represent how a quantity varies in that dimension
inside the corresponding region. The region is represented on the local
tangential projection see \cite{Astropy regions}.
